Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-10-14 F_correction.tex
[review] Some minor changes. The only major changes are highlighted, which is around Eq.26.
[referee] version resubmitted to prb.

% outer boundary correction
It is discussed in Cardy and Peschel's work\cite{cardy_finite-size_1988} that boundary will contribute a logarithmic term in the free energy,
\begin{equation}
F = - \frac{c}{6} \left( \int_M  K(x) d^2x + \int_{\partial M} k_g ds \right)  \ln L 
\end{equation}
where $M$ is a 2d smooth manifold, $K(x)$ is the Gaussian curvature, $k_g$ is the geodesic curvature of the boundary of the manifold and $L$ is the system's characteristic length.

The boundary term was not previous noticed in the literature, but is actually important even in the simplest example of the disk free energy. Consider an annulus on flat space with inner radius $r_1$ and outer radius $r_2$. Its free energy is
\begin{equation}
F({\rm annulus}) = -  \frac{c}{6} \ln \frac{r_2}{r_1} .
\end{equation}
On the other hand the free energy of a disk of radius $r_2$ is
\begin{equation}
  F( {\rm disk} ) = - \frac{c}{6} \ln \frac{r_2}{a},
\end{equation}
where $a$ is the short distance regulator. The disk free energy is completely contributed by its outer boundary with other parts being conformal invariant. In fact, $K = 0, k_g = \frac{1}{r}$ for disk, and so 
\begin{equation}
F( {\rm disk}  ) = - \frac{c}{6}  \left( \int_{\partial M} k_g ds \right)  \ln \frac{r_2}{a}  = - \frac{c}{6}  \ln \frac{r_2}{a}
\end{equation}
where $a$ is the short distance cut-off.

One can then interpret the annulus free energy as an additive contribution from its outer and inner surfaces as
\begin{equation}
F( {\rm annulus} ) = -  \frac{c}{6} \ln \frac{r_2}{a} +  \frac{c}{6} \ln \frac{r_1}{a} = - \frac{c}{6} \ln \frac{r_2}{r_1}.
\end{equation}
An annulus becomes a disk when its inner radius is of order $a$, and we can see that the contribution from the inner surface $\frac{c}{6} \ln \frac{r_1}{a}$ becomes negligible compared to the one from the outer surface.

@@

Therefore using the cylinder parameters in App.~\ref{app:lambda_12}, the $\xi$ plane and $z$ plane free energy are related through
\begin{equation}
F_{z} = F_{\xi} + \frac{c}{6} \beta .
\end{equation}
for both the fidelity and Loschmidt echo.

% staircase geometry correction
The annulus on the $\xi$ plane is called staircase geometry in Ref.~\onlinecite{cardy_finite-size_1988} due to its evolution in angular direction . The traditional radial quantization however has radial direction to be the time. One can show that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian\cite{cardy_finite-size_1988}
\begin{equation}
H_{\xi} = H_{w} - \frac{c}{24\pi} \beta .
\end{equation}
After the evolution for $2\pi$ (in the folding picture, the evolution is only $\pi$ but there are two bosons), the difference in the free energy is
\begin{equation}
F_{\xi} = F_{w} - \frac{c}{12} \beta .
\end{equation}
Gathering the two terms, we obtain the missing correction $\frac{c}{12} \beta$ between the slit and cylinder diagram, 
\begin{equation}
F_{z} = F_w + \frac{c}{12}\beta.
\end{equation}

>>>>

% outer boundary correction
It is discussed in Cardy and Peschel's work\cite{cardy_finite-size_1988} that boundary will contribute a logarithmic term in the free energy,
\begin{equation}
F = - \frac{c}{6} \left( \int_M  K(x) d^2x + \int_{\partial M} k_g ds \right)  \ln L , 
\end{equation}
where $M$ is a 2d smooth manifold, $K(x)$ is the Gaussian curvature, $k_g$ is the geodesic curvature of the boundary of the manifold and $L$ is the system's characteristic length.

The boundary term was not previous noticed in the literature, but is actually important even in the simplest example of the disk free energy. Consider an annulus on flat space with inner radius $r_1$ and outer radius $r_2$. Its free energy is
\begin{equation}
F({\rm annulus}) = -  \frac{c}{6} \ln \frac{r_2}{r_1} .
\end{equation}
On the other hand the free energy of a disk of radius $r_2$ is
\begin{equation}
  F( {\rm disk} ) = - \frac{c}{6} \ln \frac{r_2}{a},
\end{equation}
where $a$ is the short distance regulator. The disk free energy is completely contributed by its outer boundary with other parts being conformal invariant. In fact, $K = 0, k_g = \frac{1}{r}$ for disk, and so 
\begin{equation}
F( {\rm disk}  ) = - \frac{c}{6}  \left( \int_{\partial M} k_g ds \right)  \ln \frac{r_2}{a}  = - \frac{c}{6}  \ln \frac{r_2}{a} , 
\end{equation}
where $a$ is the short distance cut-off.

One can then interpret the annulus free energy as additive contributions from its outer and inner surfaces
\begin{equation}
F( {\rm annulus} ) = -  \frac{c}{6} \ln \frac{r_2}{a} +  \frac{c}{6} \ln \frac{r_1}{a} = - \frac{c}{6} \ln \frac{r_2}{r_1}.
\end{equation}
An annulus becomes a disk when its inner radius is of order $a$, and we can see that the contribution from the inner surface $\frac{c}{6} \ln \frac{r_1}{a}$ becomes negligible compared to the one from the outer surface.

@@

Therefore in both cases we should compensate $\frac{c}{6} \ln \frac{r_2}{a}$. Using the cylinder parameters in App.~\ref{app:lambda_12}, the $\xi$ plane and $z$ plane free energy are related through
\begin{equation}
F_{z} = F_{\xi} + \frac{c}{6} \beta .
\end{equation}
for both the fidelity and Loschmidt echo.

% staircase geometry correction
The annulus on the $\xi$ plane is called staircase geometry in Ref.~\onlinecite{cardy_finite-size_1988} due to its evolution in angular direction. The traditional radial quantization however has radial direction to be the time. One can show that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian\cite{cardy_finite-size_1988} of the conformal transform
\begin{equation}
H_{\xi} = H_{w} - \frac{c}{24\pi} \beta .
\end{equation}
After the evolution for $2\pi$ (in the folding picture, the evolution is only $\pi$ but there are two bosons), the difference in the free energy is
\begin{equation}
F_{\xi} = F_{w} - \frac{c}{12} \beta .
\end{equation}
Gathering the two terms, we obtain the missing correction $\frac{c}{12} \beta$ between the slit and cylinder diagram, 
\begin{equation}
F_{z} = F_w + \frac{c}{12}\beta.
\end{equation}

### 2017-10-14 analy_eval.tex
[referee] version resubmitted to prb.

We notice that there is only one apparent length scale in these diagrams -- the finite size $L$ for fidelity and imaginary time $\tau$ for the Loschmidt echo. These are the characteristic size of the corners at the tip of the slits. Regulators are necessary in keeping track of the scale dependence, otherwise a dilation transformation can rescale both $L$ and $\tau$ to $1$ and get rid of their dependence. The introduction of regulators is also physically sensible when considering the lattice realization of the systems.

We thus add small semi-circles around the points where the bcc operators reside, and then apply a series of conformal mapping.

For the fidelity case, the regulators as well as the conformal mappings are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $\xi  = \exp( \frac{\pi z}{L} ) $. The two black dots represent possible locations of boundary condition changing (bcc) operators. The dot inside the blue semi-circle has coordinate $\xi = 1$, which is the image of the point connecting $a$ and $b$ boundaries. The other dot $\xi = 0$ corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer blue semi-circle centered at $\xi = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(\xi - 1)$}
\label{fig:fidel-map}
\end{figure}
We add a small blue semi-circle to the folded strip in Fig.~\ref{fig:fidel} as the UV regulator and map it to the upper half plane using $\xi  = \exp( \frac{\pi z}{L} )$. Then both $\xi = 0$ and $1$ can host bcc operators. We assume $a = c$ such that the only bcc operator on the real axis is the one enclosed by the blue semi-circle around $\xi = 1$. In order to evaluate this diagram, we add another semi-circle centered around $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( \xi- 1)$. Finally the cylinder diagram can be viewed as path integral amplitude between the boundary state $b$ and $a$
\begin{equation}
\label{eq:partition_fun}
Z_{ab} = \langle a | e^{-\pi H } |b \rangle.
\end{equation}
where the height of the cylinder is $\pi$. The two end points of the $\epsilon$ radius semi-circle on the $z$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} .
\end{equation}
The bigger blue semi-circle intersects the real axis at $1 \pm R_{\xi}$ such that the width of the cylinder is 
\begin{equation}
\label{eq:fidel_cyd_width}
\ln R_{\xi} - \ln \frac{\pi \epsilon}{L} = \ln L + \text{constant}.
\end{equation}

The Loschmidt echo can be evaluated in the same way. Again, we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulators and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}. From $z$ plane to the $\xi$ plane, we use $\xi = \frac{z}{\tau - z}$ to map the two slits to half of an annulus, which is the same as the fidelity case. With one more conformal mapping $w = \ln \xi$, the diagram becomes the cylinder partition function between the two boundary states.

The height of the cylinder is still $\pi$ because of folding. In the $\xi$ plane, the coordinates of the two end points of the small semi-circle are $\frac{\pm \epsilon}{ \tau \mp \epsilon} \sim \frac{\pm \epsilon}{ \tau }$, while those of the larger semi-circle are $\mp \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\mp \tau}{\epsilon}$. Hence the width of the cylinder is
\begin{equation}
\label{eq:echo_cyd_width}
\ln \frac{\tau}{\epsilon} - \ln \frac{\epsilon}{\tau } = 2 \ln \tau + \text{constant}.  
\end{equation}

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{fig_H-tau_fold}
\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where imaginary time is the horizontal direction, the dashed (solid) lines are gluing (open) boundary conditions. Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state. The blue semi-circles of radius $\epsilon$ are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice). Middle: Image of the map $\xi = \frac{z}{\tau - z}$. The two semi-circles have radii $({\tau}/{\epsilon})^{\pm1}$ respectively.  Right: Image of $w = \ln \xi$. It is a cylinder by identifying the blue lines and the standard radial quantization procedure can be applied. }
\label{fig:H-tau_fold}
\end{figure}

One subtlety of the above description is that the two semi-circles in the center diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not precisely concentric. This can be resolved by the following observation. There exists conformal map $\zeta(\xi)$ that maps the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}. Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$. In our case, since the height of the cylinder is always $\pi$, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus. The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
\begin{equation}
\eta = \frac{(1 + R)^2}{(1 - R)^2}. 
\end{equation}
Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$. Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}. The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometries and thus get the leading order term in the width of the cylinders. The slight deviation to the precise concentric geometry will only bring $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to the width parameter and will not affect the fidelity and echo exponents.

\rev{Check this and the following paragraph} For the rest of this section, we should denote the width of the cylinder as $\beta$. After obtaining the partition function for the cylinder, we should set $\beta = 2 \ln L$ or $ 4 \ln \tau$ because the fidelity and Loschmidt echo are both square of the amplitudes.

The actual boundary conditions on the blue lines, which are the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, are not important in the leading order. Taking Fig.~\ref{fig:fidel-map} for example, rather than using Eq.~\eqref{eq:partition_fun}, we can alternatively view the right panel as the amplitude between the two blue boundary states $|1\rangle$ and $|2\rangle$
\begin{equation}
Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  , 
\end{equation}
where $H_{ab}$ is the Hamiltonian with boundary condition $a$ and $b$. Since $\beta$ is taken to be large, we expect that the imaginary time evolution (which is horizontal in this case) to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy is
\begin{equation}
\begin{aligned}
F &=  - \ln Z_{ab}  \sim - \ln \langle 1 |0_{ab} \rangle \langle   0_{ab}  |e^{ - \beta H_{ab}}|0_{ab} \rangle \langle 0_{ab} | 2 \rangle \\
&= \beta  E_c - \ln \langle 1| 0_{ab} \rangle  - \ln \langle 0_{ab}  |2 \rangle,
\end{aligned}
\end{equation}
where $E_c$ is the groundstate energy of $H_{ab}$. We see that different choices of the boundary conditions only change the term independent of $\beta$. Thus in the leading order we can choose any boundary condition. The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.

With these in mind, here we set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and leave the technical details to App.~\ref{app:lambda_12}. We define a set of bosonic operators related to the $a^i_n$s in Eq.~\eqref{eq:di_mode_expansion} through
\begin{equation}
\begin{aligned}
b^i_n &= \frac{a^i_n}{\sqrt{n}} \quad (b^i_n)^{\dagger} &= \frac{a^i_{-n}}{\sqrt{n}} \\
\bar{b}^i_n &= \frac{\bar{a}^i_n}{\sqrt{n}} \quad (\bar{b}^i_n)^{\dagger} &= \frac{\bar{a}^i_{-n}}{\sqrt{n}} \\
\end{aligned}
\end{equation}
for $n > 0 , i = 1, 2$, and group them compactly with the vector notation
\begin{equation}
\begin{aligned}
\vec{b}_i &= ( b^i_1, b^i_2, \cdots )^\top, \qquad \,\,\quad \vec{\bar{b}}_i = ( \bar{b}^i_1, \bar{b}^i_2, \cdots )^\top\\
\vec{b}^\dagger_i &= ( (b^i_1)^\dagger, (b^i_2)^\dagger, \cdots )^\top, \quad\vec{\bar{b}}^{\dagger}_i = ( (\bar{b}^i_1)^\dagger, (\bar{b}^i_2)^\dagger, \cdots )^\top.
\end{aligned}
\end{equation}
The boundary state in Eq.~\eqref{eq:bd_state} is then 
\begin{equation}
\exp\Big\{  (\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) R_a( \theta )   
\begin{pmatrix}
  \vec{\bar{b}}_1^{\dagger}\\
  \vec{\bar{b}}_2^{\dagger}
\end{pmatrix}\Big\}  |0  \rangle ,
\end{equation}
where $R_a( \theta ) = -S_a \otimes \mathbb{I}$. Using even a lazier notation $\vec{b} = ( \vec{b}_1, \vec{b}_2 )^\top$, we have
\begin{equation}
|a \rangle = \exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} |0 \rangle .
\end{equation}

The Hamiltonian of the folding picture has the mode expansion in terms of the $b_n$ (with periodic boundary conditions)
\begin{equation}
\begin{aligned}
  H &= \frac{2\pi}{\beta} (L_0 + \bar{L}_0) =  \frac{4\pi}{\beta}  L_0 \\
  &= \frac{4\pi}{\beta}\sum_{n > 0, i=1,2 }  n (b^i_n)^{\dagger} b^i_n \\
  &=  \frac{1}{\pi}(\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) (\mathbb{I}_2  \otimes M)
\begin{pmatrix}
  \vec{{b}_1}\\
  \vec{{b}_2}
\end{pmatrix}\\
 &= \frac{1}{\pi} \vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} ,
\end{aligned}
\end{equation}
where $L_0+ \bar{L}_0$ are the dilation operator in CFT and we have used the condition $L_0 = \bar{L}_0$ when restricted to the space of the boundary states. The infinite dimensional matrix $M$ is
\begin{equation}
M =  \frac{4\pi^2}{\beta} \text{diag}( 1, 2, \cdots ).
\end{equation}
The partition function in Eq.~\eqref{eq:partition_fun} becomes
\begin{equation}
\label{eq:Zab-bd}
\begin{aligned}
Z_{ab} =& \langle b | e^{-\pi H} | a \rangle \\
=& \langle 0 | \exp\Big\{  \vec{b} R_b( \theta )    \vec{\bar{b}} \Big\}  \exp\Big\{ -\vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} \Big\} \\
&\exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} | 0\rangle .
\end{aligned}
\end{equation}

In App.~\ref{app:lambda_12}, we obtained the leading order term in the free energy associated with Eq.~\eqref{eq:Zab-bd}. This expression is also obtained by an alternative Casimir energy calculation in App.~\ref{app:gnd_dn_lambda} for one set of the boundary conditions. A na\"ive application of the result however will lead to an apparent contradiction. One notable example is that when $a = b  = {\rm P}$, the free energy given by App.~\ref{app:lambda_12} is $- \frac{1}{12}\beta$, which should actually be {\it zero} because this is the (regularized) free energy on a plane without any interface. Physically this corresponds to the situation that the boundary condition does not change after joining the two chains. Hence the Loschmidt echo will stay at $1$ and the free energy is $0$. This motivates a shift to the free energy
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and part comes from the non-homogeneous term in the conformation transformation of the stress tensor from annulus to cylinder.

>>>>

We notice that there is only one apparent length scale in these diagrams -- the finite size $L$ for fidelity and imaginary time $\tau$ for the Loschmidt echo. These are the characteristic size of the corners at the tip of the slits. Regulators are necessary in keeping track of the scale dependence, otherwise a dilation transformation can rescale both $L$ and $\tau$ to $1$ and drop those scales. The introduction of regulators is also physically sensible when considering the lattice realization of the systems.

We thus add small semi-circles around the points where the bcc operators reside, and then apply a series of conformal mappings.

For the fidelity case, the regulators as well as the conformal maps are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $\xi  = \exp( \frac{\pi z}{L} ) $. The two black dots represent possible locations of boundary condition changing (bcc) operators. The dot inside the blue semi-circle has coordinate $\xi = 1$, which is the image of the point connecting $a$ and $b$ boundaries. The other dot $\xi = 0$ corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer blue semi-circle centered at $\xi = 1$ with radius $R_{\xi}$ to be the IR cut-off and map it to the cylinder with $w = \ln(\xi - 1)$}
\label{fig:fidel-map}
\end{figure}
We add a small blue semi-circle to the folded strip in Fig.~\ref{fig:fidel} as the UV regulator and map it to the upper half plane using $\xi  = \exp( \frac{\pi z}{L} )$. Then both $\xi = 0$ and $1$ can host bcc operators. We assume $a = c$ such that the only bcc operator on the real axis is the one enclosed by the blue semi-circle around $\xi = 1$. In order to evaluate this diagram, we add another semi-circle centered around $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to a cylinder of height $\pi$ on the right by $w = \ln ( \xi- 1)$. Finally the cylinder diagram can be viewed as an imaginary time path integral amplitude between the boundary states $b$ and $a$
\begin{equation}
\label{eq:partition_fun}
Z_{ab} = \langle a | e^{-\pi H } |b \rangle.
\end{equation}
The two end points of the $\epsilon$ radius semi-circle on the $z$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} .
\end{equation}
The bigger blue semi-circle intersects the real axis at $1 \pm R_{\xi}$ and so the width of the cylinder is 
\begin{equation}
\label{eq:fidel_cyd_width}
\ln R_{\xi} - \ln \frac{\pi \epsilon}{L} = \ln L + \text{constant}.
\end{equation}

The Loschmidt echo can be evaluated in the same way. Again, we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulators and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}. From $z$ plane to the $\xi$ plane, we use $\xi = \frac{z}{\tau - z}$ to map the two slits to half of an annulus, which is the same as the fidelity case. With one more conformal mapping $w = \ln \xi$, the diagram again becomes the cylinder partition function between the two boundary states.

The height of the cylinder is still $\pi$. In the $\xi$ plane, the coordinates of the two end points of the small semi-circle are $\frac{\pm \epsilon}{ \tau \mp \epsilon} \sim \frac{\pm \epsilon}{ \tau }$, while those of the larger semi-circle are $\mp \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\mp \tau}{\epsilon}$. Hence the width of the cylinder is
\begin{equation}
\label{eq:echo_cyd_width}
\ln \frac{\tau}{\epsilon} - \ln \frac{\epsilon}{\tau } = 2 \ln \tau + \text{constant}.  
\end{equation}

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{fig_H-tau_fold}
\caption{The dashed (solid) lines are gluing (completely reflective) boundary conditions. Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state. Left: Diagram of the Loschmidt echo that reduces to a partition function with imaginary time in the horizontal direction. The blue semi-circles of radius $\epsilon$ are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice). Middle: Image of the map $\xi = \frac{z}{\tau - z}$. The two semi-circles have radii $({\tau}/{\epsilon})^{\pm1}$ respectively.  Right: Image of $w = \ln \xi$. It is a cylinder by identifying the blue lines and the standard radial quantization procedure can be applied. }
\label{fig:H-tau_fold}
\end{figure}

One subtlety of the above description is that the two semi-circles in the center diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not precisely concentric. This can be resolved by the following observation. There exists conformal map $\zeta(\xi)$ that maps the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}. Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$. In our case, since the height of the cylinder is always $\pi$, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus. The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
\begin{equation}
\eta = \frac{(1 + R)^2}{(1 - R)^2}. 
\end{equation}
Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$. Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}. The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently use the leading order approximation to $\eta$ in the respective geometries and thus get the leading order term in the width of the cylinders. The slight deviation to the precise concentric geometry will only bring in $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to $\eta$ and the width parameter, so will not affect the fidelity and echo exponents.

For the rest of this section, we should denote the width of the cylinder as $\beta$. After obtaining the partition function on it, we should set $\beta = 2 \ln L$ or $ 4 \ln \tau$ because the fidelity and Loschmidt echo are both square of the amplitudes.

The actual boundary conditions on the blue lines, which are the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, are not important in the leading order. Taking Fig.~\ref{fig:fidel-map} for example, rather than using Eq.~\eqref{eq:partition_fun}, we can alternatively view the right panel as the amplitude between the two blue boundary states $|1\rangle$ and $|2\rangle$
\begin{equation}
Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  , 
\end{equation}
where $H_{ab}$ is the Hamiltonian with boundary condition $a$ and $b$. Since $\beta$ is taken to be large, we expect the imaginary time evolution (which is horizontal in this case) to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy is
\begin{equation}
\begin{aligned}
F &=  - \ln Z_{ab}  \sim - \ln \langle 1 |0_{ab} \rangle \langle   0_{ab}  |e^{ - \beta H_{ab}}|0_{ab} \rangle \langle 0_{ab} | 2 \rangle \\
&= \beta  E_c - \ln \langle 1| 0_{ab} \rangle  - \ln \langle 0_{ab}  |2 \rangle,
\end{aligned}
\end{equation}
where $E_c$ is the groundstate/Casimir energy of $H_{ab}$. We see that different choices of the boundary conditions only change the term independent of $\beta$. Thus in the leading order we can choose any boundary conditions. The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.

With these simplifications, we now set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$. We define a set of bosonic operators related to the $a^i_n$s in Eq.~\eqref{eq:di_mode_expansion} through
\begin{equation}
\begin{aligned}
b^i_n &= \frac{a^i_n}{\sqrt{n}} \quad (b^i_n)^{\dagger} &= \frac{a^i_{-n}}{\sqrt{n}} \\
\bar{b}^i_n &= \frac{\bar{a}^i_n}{\sqrt{n}} \quad (\bar{b}^i_n)^{\dagger} &= \frac{\bar{a}^i_{-n}}{\sqrt{n}} \\
\end{aligned}
\end{equation}
for $n > 0 , i = 1, 2$, and group them compactly with the vector notation
\begin{equation}
\begin{aligned}
\vec{b}_i &= ( b^i_1, b^i_2, \cdots )^\top, \qquad \,\,\quad \vec{\bar{b}}_i = ( \bar{b}^i_1, \bar{b}^i_2, \cdots )^\top\\
\vec{b}^\dagger_i &= ( (b^i_1)^\dagger, (b^i_2)^\dagger, \cdots )^\top, \quad\vec{\bar{b}}^{\dagger}_i = ( (\bar{b}^i_1)^\dagger, (\bar{b}^i_2)^\dagger, \cdots )^\top.
\end{aligned}
\end{equation}
The boundary state in Eq.~\eqref{eq:bd_state} is then 
\begin{equation}
\exp\Big\{  (\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) R_a( \theta )   
\begin{pmatrix}
  \vec{\bar{b}}_1^{\dagger}\\
  \vec{\bar{b}}_2^{\dagger}
\end{pmatrix}\Big\}  |0  \rangle ,
\end{equation}
where $R_a( \theta ) = -S_a \otimes \mathbb{I}$. Using even a lazier notation $\vec{b} = ( \vec{b}_1, \vec{b}_2 )^\top$, we have
\begin{equation}
\label{eq:bd_state_matrix}
|a \rangle = \exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} |0 \rangle .
\end{equation}
The matrix notation here should be understood as a bilinear expression. For example, $\vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}$ actually means $\sum_{ij}b^\dagger_iR_{ij}\bar{b}_j^\dagger$ where the dagger does not transpose the vector.

The Hamiltonian of the folding picture has the mode expansion in terms of the $b_n$ (with periodic boundary conditions)
\begin{equation}
\begin{aligned}
  H &= \frac{2\pi}{\beta} (L_0 + \bar{L}_0) =  \frac{4\pi}{\beta}  L_0 \\
  &= \frac{4\pi}{\beta}\sum_{\substack{n > 0\\ i=1,2} }  n (b^i_n)^{\dagger} b^i_n \\
  &=  \frac{1}{\pi}(\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) (\mathbb{I}_2  \otimes M)
\begin{pmatrix}
  \vec{{b}_1}\\
  \vec{{b}_2}
\end{pmatrix}\\
 &= \frac{1}{\pi} \vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} ,
\end{aligned}
\end{equation}
where $L_0+ \bar{L}_0$ are the dilation operator in CFT and we have used the condition $L_0 = \bar{L}_0$ when restricted to the space of the boundary states. The infinite dimensional matrix $M$ is
\begin{equation}
M =  \frac{4\pi^2}{\beta} \text{diag}( 1, 2, \cdots ).
\end{equation}
The partition function in Eq.~\eqref{eq:partition_fun} becomes
\begin{equation}
\label{eq:Zab-bd}
\begin{aligned}
Z_{ab} =& \langle b | e^{-\pi H} | a \rangle \\
=& \langle 0 | \exp\Big\{  \vec{b} R_b( \theta )    \vec{\bar{b}} \Big\}  \exp\Big\{ -\vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} \Big\} \\
&\exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} | 0\rangle .
\end{aligned}
\end{equation}

In App.~\ref{app:lambda_12}, we obtained the leading order term in the free energy associated with Eq.~\eqref{eq:Zab-bd}. This expression is also obtained by an alternative Casimir energy calculation in App.~\ref{app:gnd_dn_lambda} for one set of the boundary conditions. A na\"ive application of the result however will lead to an apparent contradiction. One notable example is that when $a = b  = {\rm P}$, the free energy given by App.~\ref{app:lambda_12} is $- \frac{1}{12}\beta$, which should actually be {\it zero} because this is the (regularized) free energy on a plane without any interface. Physically this corresponds to the situation that the boundary condition does not change after joining the two chains. Hence the Loschmidt echo will stay at $1$ and the free energy is $0$. This motivates a shift to the free energy
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and another part comes from the non-homogeneous term in the conformation transformation of the stress tensor from annulus to cylinder.
